### 2021-02-13 yfcc100m/paper/vldb2021/eval.tex
Update queries on eval.tex

To evaluate the access to metadata and images,
we use the following queries, modeled after our internal use cases:
\begin{itemize}
\item \textit{q1} - {\bf {\em 1tag}}: Find metadata/images with one specific autotag (i.e. alligator, lake, etc).
\item \textit{q2} - {\bf {\em 1tag\_resize}}: Find metadata/images with one specific autotag and resize to 224x224.
\item \textit{q3} - {\bf {\em 1tag\_resize\_geo}}: Find metadata/images with one specific autotag, resize to 224x224, and in a particular geo-location (with a 20 degrees radius in latitude and longitude).
\item \textit{q4} - {\bf {\em 2tag\_resize\_geo\_and}}: Find metadata/images with two specific autotags (i.e. alligator AND lake), resize to 224x224, and in a particular geo-location (with a 20 degrees radius in latitude and longitude).
\item \textit{q5} - {\bf {\em 2tag\_resize\_geo\_or}}: Find metadata/images with either of two specific autotags (i.e. alligator OR lake), resize to 224x224, and in a particular geo-location (with a 20 degrees radius in latitude and longitude).
\end{itemize}

>>>>

To evaluate the access to metadata and images,
we use the following queries, modeled after our internal use cases:

\begin{itemize}
\item \textit{q1} - {\bf {\em 1tag\_resize}}: Retrieve images with one specific autotag and resize to 224x224.

\item \textit{q2} - {\bf {\em 1tag\_geo\_resize}}: Retrieve images with one specific autotag, in a particular geo-location, and resize to 224x224,.

\item \textit{q3} - {\bf {\em 2tag\_and\_resize}}: Retrieve images with two specific autotags (i.e. alligator AND lake), and resize to 224x224.

\item \textit{q4} - {\bf {\em 2tag\_or\_resize}}: Retrieve images with either of two specific autotags (i.e. alligator OR lake), and resize to 224x224.

\item \textit{q5} - {\bf {\em 2tag\_resize\_geo\_and}}: Retrieve images with two specific autotags (i.e. alligator AND lake), in a particular geo-location, and resize to 224x224.

\item \textit{q6} - {\bf {\em 2tag\_resize\_geo\_or}}: Retrieve images with either of two specific autotags (i.e. alligator OR lake), in a particular geo-location, and resize to 224x224.

\end{itemize}
